---
title: "Homework 2"
author: "Sergi Carol & Mikael"
date: "October 8, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## example2 ANCOVA

```{r echo=FALSE}
library(ggplot2)
library(car) 
library(MASS)

load("ais.Rdata")
load("birthw.RData")

attach(ais)
model2<-lm(pcBfat~ssf+sex)
res2<-stdres(model2)

ais[which(res2>3),]
ais2<-ais[-which(res2>3),]

model4<-lm(log(pcBfat)~log(ssf)+sex, data=ais2)
summary(model4)

plot(fitted(model4),stdres(model4))
res2<-stdres(model4)
```

```{r}
summary(model4)
```

#### Deduce which is the change in the pcBfat by changing one unit the ssf?

From the summary of the model we can see how the estimated forumla predicted from the liniar model is as follows, in the case of a male (since the female is the baseline case we would ommit the -2.96 parameter):

log(_pcbFat) = - 0.80288 * log(ssf) - 0.23584 * sexm + e_

This means that every change of unit of _ssf_ augments the vaue of __pcbFat__ by e^0.80288, which is 2.232 .


#### Which is the pcBfat predicted for a male with a ssf of 54? and Which is the pcBfat predicted for a female with a sff of 48?

To do so we will create a dataframe with the values we want to predict, and then I will predict the outcome using the liniar model we have created.
```{r}
ssf_data <- data.frame(ssf = c(54, 48), sex = c('m', 'f'))
res <- predict.lm(model4, newdata=ssf_data)
names(res) <- c("male", "female")
res <- exp(res)
res
```
In the case of a male with a value of SSF of 54 we get a predicted pcbFat value of 9.617927.

In the case of a female with a value of SSF of 48 we get a predicted pcbFat value of 11.044816.

#### Which has to be the ssf of a male in order to have a pcBfat of 14.7? and for a female?
To do so we will create a new model (model 5) with the __ssf__ as the target attribute, which will be calculated using pcBfat and sex.
```{r}
model5 <- lm(ssf ~ pcBfat+sex, data=ais2)
summary(model5)

pcBfat_data <- data.frame(pcBfat = c(14.7, 14.7), sex=c('m', 'f'))
res <- predict.lm(model5, newdata=pcBfat_data)
plot(fitted(model5),stdres(model5))
```

As what happend with model 2 and 3, we see how the residuals are not between -2 and 2, thus we will apply the same concept of model4, using a log scale.
```{r}
model5 <- lm(log(ssf) ~ log(pcBfat)+sex, data=ais2)
summary(model5)

pcBfat_data <- data.frame(pcBfat = c(14.7, 14.7), sex=c('m', 'f'))
res <- predict.lm(model5, newdata=pcBfat_data)
plot(fitted(model5),stdres(model5))
names(res) <- c("male", "female")
res <- exp(res)
res
```
Although we still have some residuals over 2, we can accept this results, since all the other metrics indicate that this is indeed a good model.

As we can see the predicted outcomes for the target attribute _ssf_ are _86.787_ and _68.5134_

#### Interpred the standard error value.

```{r}
summary(model4)
```
From the residual standard error value we can gather information about how good our model is, in this case we have a really low residual error which is a good indicator, meaning that our model is really good. If we take a closer look at the residuals we see how we are moving between an 0.2 error from the mean.